\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-17 paper/paper 2/dc-2015.tex
introduction

The creation of such mappings is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates. 
The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES. Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be used to formulate the constraint that publications must have at least one author which must be a person. This constraint can be expressed as follows using different constraint languages:

@@

Note that the SPIN representation is NOT a mapping, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated. The mapping for DSP is much more complicated and can be found in the mappings provided by us\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.

>>>>

The creation of such mappings is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates. \tb{diese beipsiel zeigt nur wie constraints desslben typs mit unterschiedlichen CL ausgedrückt wird! sollen wir hier noch ein codebeipsiel eines konkreten mappings dieses CT für DSP zeigen?}
The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES. Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be used to formulate the constraint that publications must have at least one author which must be a person. This constraint can be expressed as follows using different constraint languages:

@@

Note that the SPIN representation is NOT a mapping, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated. The mappings for OWL 2 and DSP are much more complicated and can be found in the mappings provided by us\footnote{OWL 2 mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/OWL2_SPIN-Mapping.ttl}; DSP mapping online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.
